\documentclass[10pt,a4paper]{scrartcl}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}

\newsavebox{\mybox}
\newenvironment{apiCode}[1]
{ \begin{lrbox}{\mybox} \begin{minipage}{0.9\textwidth} {\color{Mahogany} \small\texttt{#1}} \vspace{8pt} \newline }
{ \end{minipage} \end{lrbox}\fbox{\usebox{\mybox}} \newline\vspace{4pt}\newline }

\title{Scripting API}
\subtitle{for Evilly Evil Villains 1.0}
\author{Alexis Breust}
\date{\today}

\begin{document}
\maketitle

\section{Basics and concepts}
\subsection{Comments}
A commented line start with a \texttt{\#}, anything else on the line is ignored. Empty lines are also ignored. However if you let a non-commented line with any character like just a space, this will be interpreted as a command and the script will loop silently trying desperately to execute it.

\subsection{Tools}
\begin{apiCode}{wait $N$}
Pause the script reading for $N$ milliseconds.\newline
\textit{That function only works for input scripts (specified as application argument).}
\end{apiCode}

\section{Dungeon design}
\subsection{Top-level functions}
\subsubsection{Structure control}
\begin{apiCode}{dungeon structure floorsCount (add|set) $N$}
Change the floors count.
\begin{itemize}
\itemsep 0em
\item If \verb#add#, the floors count is added $N$ floors. $N$ can be negative.
\item If \verb#set#, the floors count is set to $N$ floors.
\end{itemize}
\end{apiCode}
\begin{apiCode}{dungeon structure floorRoomsCount (add|set) $N$}
Change the rooms count on each floor.
\begin{itemize}
\itemsep 0em
\item If \verb#add#, the rooms count on each floor is added $N$ rooms. $N$ can be negative.
\item If \verb#set#, the rooms count on each floor is set to $N$ rooms.
\end{itemize}
\end{apiCode}

\subsubsection{Generics control}
\begin{apiCode}{dungeon generic monsters unlock (*|$MonsterID$) [free]}
Unlock a monster of a generic.
\begin{itemize}
\itemsep 0em
\item If \verb#*#, unlock all monsters.
\item If the monster is already unlocked, nothing happens.
\item If \verb#free# is indicated, the player won't pay anything,\newline
	  otherwise if the player cannot afford the unlock tax, nothing happens.
\end{itemize}
\end{apiCode}
\begin{apiCode}{dungeon generic traps unlock (*|$TrapID$) [free]}
Unlock a trap of a generic.
\begin{itemize}
\itemsep 0em
\item If \verb#*#, unlock all traps.
\item If the trap is already unlocked, nothing happens.
\item If \verb#free# is indicated, the player won't pay anything,\newline
	  otherwise if the player cannot afford the unlock tax, nothing happens.
\end{itemize}
\end{apiCode}

\subsubsection{Rooms location}
\begin{apiCode}{dungeon room $X_1$ $X_2$ ...}
Locate the room at position $(X_1, X_2)$.\newline
\textit{One need to complete the command with some other action on the located room.}
\end{apiCode}
\begin{apiCode}{dungeon rooms ...}
Locate all the rooms of the dungeon as a multiple rooms set.\newline
\textit{One need to complete the command with some other action on the located multiple rooms.}
\end{apiCode}

\subsection{Multiple rooms control}
\begin{apiCode}{...\{rooms\}... foreach ...}
For all rooms, apply a located room command.\newline
\textit{One need to complete the command with some other action on each located room.}
\end{apiCode}
%\begin{apiCode}{...\{rooms\}... keep constructed ...}
%Filter the rooms to keep only the constructed ones.\newline
%\textit{One need to complete the command with some other action on the located multiple rooms.}
%\end{apiCode}

\subsection{Room control}
\begin{apiCode}{...\{room\}... construct [free]}
Construct the room.
\begin{itemize}
\itemsep 0em
\item If the specified room is already contructed, nothing happens.
\item If \verb#free# is indicated, the player won't pay anything,\newline
	  otherwise if the player cannot afford the room creation tax, nothing happens.
\end{itemize}
\end{apiCode}
\begin{apiCode}{...\{room\}... destroy [loss]}
Destroy the room.
\begin{itemize}
\itemsep 0em
\item If the specified room is not constructed yet, nothing happens.
\item If \verb#loss# is indicated, the player won't get resources back.
\end{itemize}
\end{apiCode}
\begin{apiCode}{...\{room\}... push (north|south|west|east) [$T$]}
Push from the room into the specified direction.\newline
The animation will be $T$ milliseconds long (defaulting to $250ms$ if not specified).
\begin{itemize}
\itemsep 0em
\item If the specified room is not constructed yet, nothing happens.
\item If there is no constructed room from the specified room\newline
	  into the direction, nothing happens.
\end{itemize}
\end{apiCode}
\begin{apiCode}{...\{room\}... trap ...}
Locate the trap in the room.\newline
\textit{One need to complete the command with some other action on the located trap.}
\begin{itemize}
\itemsep 0em
\item If the specified room is not constructed yet, nothing happens.
\end{itemize}
\end{apiCode}
\begin{apiCode}{...\{room\}... facilities ...}
Locate the facilities in the room.\newline
\textit{One need to complete the command with some other action on the located facilities.}
\begin{itemize}
\itemsep 0em
\item If the specified room is not constructed yet, nothing happens.
\end{itemize}
\end{apiCode}

\subsection{Trap control}
\begin{apiCode}{...\{trap\}... set $TrapID$ [free]}
Set the trap to $TrapID$.
\begin{itemize}
\itemsep 0em
\item If the trap is already a $TrapID$, nothing happens.
\item If \verb#free# is indicated, the player won't pay nor get resources back,\newline
	  otherwise if the player cannot afford the trap creation tax, nothing happens.
\item If the trap is not set yet, it will be removed first, giving back resources if not \verb#free#.
\end{itemize}
\end{apiCode}
\begin{apiCode}{...\{trap\}... remove [loss]}
Remove the trap.
\begin{itemize}
\itemsep 0em
\item If the trap is not set yet, nothing happens.
\item If \verb#loss# is indicated, the player won't get resources back.
\end{itemize}
\end{apiCode}

\subsection{Facilities control}
\begin{apiCode}{...\{facilities\}... create $FacilityID$ [free]}
Create the facility $FacilityID$.
\begin{itemize}
\itemsep 0em
\item If there already is a facility $FacilityID$, nothing happens.
\item If \verb#free# is indicated, the player won't pay anything,\newline
	  otherwise if the player cannot afford the facility creation tax, nothing happens.
\end{itemize}
\end{apiCode}
\begin{apiCode}{...\{facilities\}... remove $FacilityID$ [loss]}
Remove the facility $FacilityID$.
\begin{itemize}
\itemsep 0em
\item If there is no facility $FacilityID$, nothing happens.
\item If \verb#loss# is indicated, the player won't get resources back.
\end{itemize}
\end{apiCode}
\begin{apiCode}{...\{facilities\}... find $FacilityID$ ...}
Locate a facility $FacilityID$.\newline
\textit{One need to complete the command with some other action on the located facility.}
\begin{itemize}
\itemsep 0em
\item If the located facility does not exist, nothing happens.
\end{itemize}
\end{apiCode}

\subsubsection*{Facility control}
\begin{apiCode}{...\{facility\}... ai $FuncName$}
Calls the function $FuncName$ from the Artificial Intelligence file (\texttt{ai.lua}).
\begin{itemize}
\itemsep 0em
\item If the specified function does not exist, nothing happens.
\end{itemize}
\end{apiCode}
\begin{apiCode}{...\{facility\}... link set $Y_1$ $Y_2$}
Set the link of the located facility to the room at position $(Y_1, Y_2)$.
\end{apiCode}

\end{document}
